Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-05 Paper/app.tex
..

In Figure~\ref{fig:hd}, we illustrate the resulting eigenvalue spectrum and the sufficient summary 
plot.
%
\begin{figure}[htbp]
 \begin{center}
   \includegraphics[width=0.45\textwidth]{./Figures/eig_33D}
   \includegraphics[width=0.45\textwidth]{./Figures/ssp_33D}
\caption{Left: Eigenvalue spectrum of $\hat{\mat{C}}$. Right: Sufficient summary plot indicating the
existence of a potential 1-dimensional active subspace.} 
\label{fig:hd}
\end{center}
\end{figure}
%
The second eigenvalue is observed to be roughly four orders of magnitude smaller than the first 
indicating the existence of a 1-dimensional active subspace. This is further confirmed by the sufficient
summary plot which shows that the variability in $G$ can be approximated using a 1-dimensional regression
fit which could be used as a surrogate. We will verify the accuracy of the surrogate later in~\ref{sub:verify}.

@@

The 1-dimensional surrogate ($\mathcal{Y}$) is investigated for its accuracy as well as the ability to capture the 
uncertainty in the
model output in two ways. Firstly, we estimate the relative L-2 norm of the discrepancy~($\varepsilon_d$)
between estimates of ignition delay in the case of H$_2$/O$_2$ reaction, obtained using the 
model output and the surrogate in the following equation:
%
\be
\varepsilon_d = \frac{\|f(\bm{\theta}) - \mathcal{Y}(\bm{\xi})\|_2}{\|f(\bm{\theta})\|_2}
\ee
%
The relative norm, $\varepsilon_d$ was estimated to be 8.92$\times10^{-2}$ based on a validation test data
comprising 1000 model evaluations. Hence, in the norm-sense, it can be said that the 1-dimensional surrogate is 
reasonably accurate.

>>>>

In Figure~\ref{fig:hd}, we illustrate the resulting eigenvalue spectrum and the SSP.
%
\begin{figure}[htbp]
 \begin{center}
   \includegraphics[width=0.45\textwidth]{./Figures/eig_33D}
   \includegraphics[width=0.45\textwidth]{./Figures/ssp_33D}
\caption{Left: Eigenvalue spectrum of $\hat{\mat{C}}$. Right: SSP of the computed active subspace, and the
corresponding 1-D linear fit.} 
\label{fig:hd}
\end{center}
\end{figure}
%
The second eigenvalue is observed to be roughly four orders of magnitude smaller than the first 
indicating the existence of a 1-dimensional active subspace. This is further confirmed by the SSP
 which shows that the variability in $G$ can be approximated using a 1-dimensional regression
fit ($\tilde{G}$) which could be used as a surrogate. A linear, quadratic, and a cubic fit to the SSP was performed.
The linear fit illustrated in Figure~\ref{fig:hd} (right) was found to be the most accurate. In~\ref{sub:verify},
we investigate the accuracy of the 1D surrogate based on the linear fit by estimating the relative L-2
norm of its discrepancy with model evaluations at an independent set of samples, and by comparing the
respective probability distributions.

@@

The 1-dimensional surrogate ($\tilde{G}$) is investigated for its accuracy as well as the ability to capture the 
uncertainty in the
model output in two ways. Firstly, we estimate the relative L-2 norm of the discrepancy~($\varepsilon_d$)
between estimates of ignition delay in the case of H$_2$/O$_2$ reaction, obtained using the 
model output and the surrogate in the following equation:
%
\be
\varepsilon_d = \frac{\|G(\bm{\xi}) - \tilde{G}(\bm{\xi})\|_2}{\|G(\bm{\xi})\|_2}
\ee
%
The relative norm, $\varepsilon_d$ was estimated to be 8.50$\times10^{-2}$ based on a validation test data
comprising 1000 model evaluations. Hence, in the norm-sense, it can be said that the 1-dimensional surrogate is 
reasonably accurate.
